---
title: "Results EC50 assay 2 for MTZ 9-11.8.19"
author: "Sascha Krakovka"
#date: "`r Sys.Date()`"
output: 
html_notebook:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    df_print: paged
    code_folding: hide
    fig_width: 6
    fig_height: 6
---


```{r , include=FALSE}
#Call for the needed libraries in order of usage
library(tidyverse)
library(DT)
library(modelr)
options(na.action = na.warn)
library(knitr)
opts_knit$set(progress = FALSE, verbose = FALSE)
opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE)
library(tinytex)
```
#THIS IS THE NEW SETUP
#Introduction
#####25.3.19
I chose to give every concentration a DMSO control with the same amount DMSO.

#Experiment set-up - IC50 measurement
#####26.3.19
1. Chill trophozoits on ice for 15min, detach by hitting
2. Enumerate cells in Neubauer chamber (average x2x10 000) 
3. Dilute to 10 cells/?l (=$1*10^{4} cells/ml$) for WB and C60.5, 20 cells/?l (=$2*10^{4} cells/ml$) for C6a! and C60.5
4. Seed with 40?l of these in 2 96-well plates
5. Put with an anaerobic pouch into an anaerobic sachet
6. Incubate @37?C for 2h
7. Add 160?l TYDK with the drug of choice for the correct final C 
8. Back into sachet with new anaerobic pouch
9. Incubate for 48h 

#####28.3.19
10. Thaw GloTiter reagent 1h before use
11. Equilibrate plates to RT for 30min
12. Add 50?l of reagent to wells
13. Shake for 10min @RT
14. Incubate 10 min @ RT
15. Luminescence measured in Tecan


#Results
`r Sys.Date()`
```{r}
#Now come a lot of operations without text in the output file 
#Read your file in
df <- read_csv2("EC50MTZ_12_9_19_1.csv")
#kable(df)

```


```{r}
#Calculate the background according to plate set-up
#read find the correct function for my word and include it into this or make it a csv
Background <-(df[2,4]+df[3,5]+df[4,6]+df[5,7])/4
#print(Background)
```


```{r}
#Distract the background from all values in my matrix
ndf <-df[2:7,2:12]-Background[1,1]
```


```{r}
#Extract WB values according to plate set-up

ZeroWB <- (ndf[1,2]+ndf[5,6])/2
OneWB <- (ndf[3,2])
OneWBZ <- ndf[2,2]

TwoWB <- (ndf[5,2])
TwoWBZ <- (ndf[4,2])

FiveWB <- (ndf[1,6])
FiveWBZ <- (ndf[6,2])

TenWB <- (ndf[3,6])
TenWBZ <- (ndf[2,6])

TwentyWB <- (ndf[1,10])
TwentyWBZ <- (ndf[6,6])

FiftyWB <- (ndf[5,10])
FiftyWBZ <- (ndf[3,10])
```


```{r}
#Extract C6NR values according to plate set-up

ZeroC6NR <- (ndf[2,3]+ndf[3,7])/2
OneC6NR <- (ndf[4,3])
OneC6NRZ <- ndf[3,3]

TwoC6NR <- (ndf[6,3])
TwoC6NRZ <- (ndf[5,3])

FiveC6NR <- (ndf[2,7])
FiveC6NRZ <- (ndf[1,7])

TenC6NR <- (ndf[5,7])
TenC6NRZ <- (ndf[4,7])

TwentyC6NR <- (ndf[1,11])
TwentyC6NRZ <- (ndf[6,7])

FiftyC6NR <- (ndf[5,11])
FiftyC6NRZ <- (ndf[3,11])
```


```{r}
#Extract C60.5 values according to plate set-up

ZeroC60.5 <- (ndf[1,4]+ndf[3,8])/2
OneC60.5 <- (ndf[4,4])
OneC60.5Z <- ndf[3,4]

TwoC60.5 <- (ndf[6,4])
TwoC60.5Z <- (ndf[5,4])

FiveC60.5 <- (ndf[2,8])
FiveC60.5Z <- (ndf[1,8])

TenC60.5 <- (ndf[5,8])
TenC60.5Z <- (ndf[4,8])

TwentyC60.5 <- (ndf[2,10])
TwentyC60.5Z <- (ndf[6,8])

FiftyC60.5 <- (ndf[6,10])
FiftyC60.5Z <- (ndf[4,10])
```


```{r}
#Extract C6aI values according to plate set-up

ZeroC6aI <- (ndf[1,5]+ndf[3,9])/2
OneC6aI <- (ndf[4,5])
OneC6aIZ <- ndf[2,5]

TwoC6aI <- (ndf[6,5])
TwoC6aIZ <- (ndf[5,5])

FiveC6aI <- (ndf[2,9])
FiveC6aIZ <- (ndf[1,9])

TenC6aI <- (ndf[5,9])
TenC6aIZ <- (ndf[4,9])

TwentyC6aI <- (ndf[2,11])
TwentyC6aIZ <- (ndf[6,9])

FiftyC6aI <- (ndf[6,11])
FiftyC6aIZ <- (ndf[4,11])
```

###Survival of strains WB, C6NR, C60.5 and C6aI under the tested drug with the given concentrations
```{r}
#Calculate percentages for survival of all strains for the drug tested to have a clear table
Percent_survival_drug <- tribble(
  ~"Strain",~"0uM[%]",  ~"1uM[%]", ~"2uM[%]", ~"5uM[%]", ~"10uM[%]", ~"20uM[%]", ~"50uM[%]",
  #--|--|------
  "WB", ZeroWB/ZeroWB*100, OneWB/OneWBZ*100, TwoWB/TwoWBZ*100, FiveWB/FiveWBZ*100, TenWB/TenWBZ*100, TwentyWB/TwentyWBZ*100, FiftyWB/FiftyWBZ*100,
  
  "C6NR", ZeroC6NR/ZeroC6NR*100, OneC6NR/OneC6NRZ*100, TwoC6NR/TwoC6NRZ*100, FiveC6NR/FiveC6NRZ*100, TenC6NR/TenC6NRZ*100, TwentyC6NR/TwentyC6NRZ*100, FiftyC6NR/FiftyC6NRZ*100,
  
  "C60.5",ZeroC60.5/ZeroC60.5*100, OneC60.5/OneC60.5Z*100, TwoC60.5/TwoC60.5Z*100, FiveC60.5/FiveC60.5*100, TenC60.5/TenC60.5Z*100, TwentyC60.5/TwentyC60.5Z*100, FiftyC60.5/FiftyC60.5Z*100,
  
  "C6aI", ZeroC6aI/ZeroC6aI*100, OneC6aI/OneC6aIZ*100, TwoC6aI/TwoC6aIZ*100, FiveC6aI/FiveC6aIZ*100, TenC6aI/TenC6aIZ*100, TwentyC6aI/TwentyC6aIZ*100, FiftyC6aI/FiftyC6aIZ*100
)
kable(Percent_survival_drug)
write_csv(Percent_survival_drug, path = "Percent_survival_MTZ_1.csv")
```


```{r}
#Tribble for easier plotting with one column for C and one for each strain 
MTZ_1 <- tribble(
  ~"Conc", ~"WB", ~"C6NR", ~"C60.5", ~"C6aI", 
   #--|--|----
  1e-20, ZeroWB/ ZeroWB*100, ZeroC6NR/ ZeroC6NR*100, ZeroC60.5/ ZeroC60.5*100, ZeroC6aI/ ZeroC6aI*100,
  
  1, OneWB/ OneWBZ*100, OneC6NR/ OneC6NRZ*100, OneC60.5/ OneC60.5Z*100, OneC6aI/ OneC6aIZ*100,
  
  2,  TwoWB/ TwoWBZ*100, TwoC6NR/TwoC6NRZ*100, TwoC60.5/ TwoC60.5Z*100, TwoC6aI/TwoC6aIZ*100,
  
  5, FiveWB/ FiveWBZ*100, FiveC6NR/ FiveC6NRZ*100, FiveC60.5/ FiveC60.5Z*100, FiveC6aI/ FiveC6aIZ*100,
  
  10, TenWB/ TenWBZ*100, TenC6NR/ TenC6NRZ*100, TenC60.5/ TenC60.5Z*100, TenC6aI/ TenC6aIZ*100,
  
  20, TwentyWB/ TwentyWBZ*100, TwentyC6NR/ TwentyC6NRZ*100, TwentyC60.5/ TwentyC60.5Z*100, TwentyC6aI/ TwentyC6aIZ*100,
  
  50, FiftyWB/ FiftyWBZ*100, FiftyC6NR/ FiftyC6NRZ*100, FiftyC60.5/ FiftyC60.5Z*100, FiftyC6aI/ FiftyC6aIZ*100
)
#print(MTZ_1)
write_csv(MTZ_1, path = "MTZ_5.csv")
```


##A visualisation of the values
```{r}
#See how it looks. Here you can play with the graphs

# Plot it 
ggplot(MTZ_1)+
    labs(title ="IC50 MTZ")+
    ylab("Procent survival MTZ")+
    xlab("Concentration metronidazole in ?M")+
    theme(plot.caption = element_text(size = 11))+
    geom_point (mapping = aes(x = Conc, y = WB), color="red")+
    geom_point (mapping = aes(x = Conc, y = C6NR), color="blue")+
    geom_point (mapping = aes(x = Conc, y = C60.5), color="green")+
    geom_point (mapping = aes(x = Conc, y = C6aI), color="black")+ 
    stat_smooth(mapping = aes(x = Conc, y = WB), color="red", formula = y ~log10(x))+
    stat_smooth(mapping = aes(x = Conc, y = C6NR), color="blue", formula = y ~log10(x))+
    stat_smooth(mapping = aes(x = Conc, y = C60.5), color="green", formula = y ~log10(x))+
    stat_smooth(mapping = aes(x = Conc, y = C6aI), color="black", formula = y ~log10(x))+
    theme_bw() +
    #scale_y_continuous(limits = c(5,100), trans = "log")+
    scale_y_continuous(limits = c(0.1,100))+
    scale_x_continuous(limits = c(0, 50))
    #scale_x_continuous(limits = c(1, 50), trans = "log")
   
```

##Resulting IC50 values for the strains tested under our drug concentrations

```{r}
#Calculate the model for WB
 modelWB <- lm(log(WB)~Conc, data = MTZ_1)

#summary(modelWB)
fWB <- round(coef(modelWB) ,2)

eqWB <- paste0("y = ", fWB[1],
             ifelse(sign(fWB[2])==1, " + ", " - "), abs(fWB[2]), " Conc ")

eWB <- round(solve(fWB[2], log(50)-fWB[1]) ,2)

EC50WB <- paste0("EC50[?M] = ", eWB[1])

ggplot(MTZ_1) + 
    ylab("Procent survival MTZ WB") + 
    geom_point (mapping = aes(x = Conc, y = WB), color="red")+
    theme_bw() +
    scale_x_continuous(limits = c(0, 50)) +
    scale_y_continuous(limits = c(0.1,115),trans = "log")+
    stat_smooth(aes(x = Conc, y = WB), method="lm", color="red")+
    annotate(geom="text", x=30, y=30, label=eqWB,
              color="black")+
    annotate(geom="text", x=40, y=10, label=EC50WB,
              color="black")

#Calculate the model for C6NR
 modelC6NR <- lm(log(C6NR)~Conc, data = MTZ_1)

#summary(modelC6NR)
fC6NR <- round(coef(modelC6NR) ,2)

eqC6NR <- paste0("y = ", fC6NR[1],
             ifelse(sign(fC6NR[2])==1, " + ", " - "), abs(fC6NR[2]), " Conc ")

eC6NR <- round(solve(fC6NR[2], log(50)-fC6NR[1]) ,2)

EC50C6NR <- paste0("EC50[?M] = ", eC6NR[1])

ggplot(MTZ_1) + 
    ylab("Procent survival MTZ C6NR") + 
    geom_point (mapping = aes(x = Conc, y = C6NR), color="blue")+
    theme_bw() +
    scale_x_continuous(limits = c(0, 50)) +
    scale_y_continuous(limits = c(0.1,115),trans = "log")+
    stat_smooth(aes(x = Conc, y = C6NR), method="lm", color="blue")+
    annotate(geom="text", x=30, y=30, label=eqC6NR,
              color="black")+
    annotate(geom="text", x=40, y=10, label=EC50C6NR,
              color="black")

#Calculate the model for C60.5
 modelC60.5 <- lm(log(C60.5)~Conc, data = MTZ_1)

#summary(modelC60.5)
fC60.5 <- round(coef(modelC60.5) ,2)

eqC60.5 <- paste0("y = ", fC60.5[1],
             ifelse(sign(fC60.5[2])==1, " + ", " - "), abs(fC60.5[2]), " Conc ")

eC60.5 <- round(solve(fC60.5[2], log(50)-fC60.5[1]) ,2)

EC50C60.5 <- paste0("EC50[?M] = ", eC60.5[1])

ggplot(MTZ_1) + 
    ylab("Procent survival MTZ C60.5") + 
    geom_point (mapping = aes(x = Conc, y = C60.5), color="green")+
    theme_bw() +
    scale_x_continuous(limits = c(0, 50)) +
    scale_y_continuous(limits = c(0.1,115),trans = "log")+
    stat_smooth(aes(x = Conc, y = C60.5), method="lm", color="green")+
    annotate(geom="text", x=30, y=5, label=eqC60.5,
              color="black")+
    annotate(geom="text", x=40, y=2, label=EC50C60.5,
              color="black")

#Calculate the model for C6aI
 modelC6aI <- lm(log(C6aI)~Conc, data = MTZ_1)

#summary(modelC6aI)
fC6aI <- round(coef(modelC6aI) ,2)

eqC6aI <- paste0("y = ", fC6aI[1],
             ifelse(sign(fC6aI[2])==1, " + ", " - "), abs(fC6aI[2]), " Conc ")

eC6aI <- round(solve(fC6aI[2], log(50)-fC6aI[1]) ,2)

EC50C6aI <- paste0("EC50[?M] = ", eC6aI[1])

ggplot(MTZ_1) + 
    ylab("Procent survival MTZ C6aI") + 
    geom_point (mapping = aes(x = Conc, y = C6aI), color="black")+
    theme_bw() +
    scale_x_continuous(limits = c(0, 50)) +
    scale_y_continuous(limits = c(0.1,115),trans = "log")+
    stat_smooth(aes(x = Conc, y = C6aI), method="lm", color="black")+
    annotate(geom="text", x=30, y=5, label=eqC6aI,
              color="black")+
    annotate(geom="text", x=40, y=2, label=EC50C6aI,
              color="black")

EC50valuesMTZ_1_8_8_19 <- tribble(
   ~" ", ~"WB", ~"C6NR", ~"C60.5", ~"C6aI", 
   #--|--|----
  "EC50[?M]", eWB, eC6NR, eC60.5, eC6aI)

kable(EC50valuesMTZ_1_8_8_19)
write_csv(EC50valuesMTZ_1_8_8_19, path = "EC50MTZ_1_12_9_19.csv")
```



#Dicussion and conclusion
Talk about what these results mean and what the next steps are 


